MSB104_assignment1

### 2023-10-10 MSB104_assignment1.qmd
Update 10.10.23

As mentioned earlier, the data include numbers from NUTS3 level

Som beskrevet over inneholder tallene fra NUTS3 level disse dataene.
Vi bestemte oss for å dele Tyskland inn i Nord og Sør pga.
(se comments).

Gå gjennom outliers ved å bruke Espen sitt tilsendte dokument.
F.eks.
beskrive Wolfsbrug, Hamburg etc.
Beskriv de laveste, si noe om hvorfor dette er tilfelle.

Beskrive finanskrisen og Covid i grafen.

Beskrive deskriptiv statistikk.

>>>>

In order to achieve a presentable figure showing GDP per year for the German sub-regions, we decided to divide the data into Northern and Southern Germany.
This prevented the data from becoming overly clustered and improved our ability to interpret the graphs.
The first figure presents data for North Germany, and the second figure presents data for South Germany.

In the figure presenting GDP per year for sub-regions in North Germany, we can observe one graph in particular on the top.
This graph also correspond to the max value seen in the table containing summary statistics.
This is the graph for region DE60, which is the code for Hamburg.
In 2000, Hamburg had a GDP per capita 45 659.50

2020:

DE60, Hamburg, 64 366.49

DE91, Braunschweig (Wolfsburg), 48 156.71

DE50, Bremen, 47 816.62

According to the datasets we used from Eurostat to calculate the GDP per capita, the sub-region in Germany with the highest GDP per capita was the sub-region coded DE913.
According to the report "Statistical regions in the European Union and partner countries NUTS and statistical regions 2021", this region is Wolfsburg, Kreisfreie Stadt **(SOURCE).** In 2019, each inhabitant stood for an economic output of about 196 010.74 euros.
Wolfsburg is the home of the car manufacturer group Volkswagen, which gives the local population job opportunities.
**Weernink (1997)** states that Volkswagen employees enjoy higher average wages, contributing to a higher GDP per capita, contributing to investment in education, infrastructure and health care, which enhances the overall quality of life for residents.
On the other hand, the sub-region with the lowest GDP per capita was Südwestpfalz (DEB3K).
This might be due to the limitation of industries that provide employees with high productivity or wages.
Another reasons can be income inequality, lack of investments (**SOURCE**)

**Gå gjennom outliers ved å bruke Espen sitt tilsendte dokument. F.eks. beskrive Wolfsbrug, Hamburg etc. Beskriv de laveste, si noe om hvorfor dette er tilfelle. Koble opp mot deskriptiv statistikk.**

**Si noe om finanskrisen og Covid i grafen.**

Remote or rural areas may have fewer economic opportunities and lower GDP per capita compared to urban centers.

Infrastructure and Education: Insufficient infrastructure and educational resources can hinder economic development.
Lack of access to quality education and transportation infrastructure can limit a region's ability to attract businesses and create high-paying jobs.

Income Inequality: Even if there are pockets of wealth in a region, high levels of income inequality can result in a low average GDP per capita.
This means that a significant portion of the population earns a relatively low income.

Government Policies: Government policies, taxation, and public investments can influence regional economic development.
Regions with supportive policies and investments in education, healthcare, and infrastructure tend to perform better economically.

Demographic Factors: The age and size of the population can also impact GDP per capita.
Regions with an aging population may have higher healthcare costs and lower labor force participation, affecting economic output.

Historical Factors: Historical events, such as wars or economic crises, can have long-lasting effects on a region's economy.
To understand the specific reasons behind Südwestpfalz's low GDP per capita, it would be necessary to conduct a detailed economic analysis and consider current economic conditions, local policies, and other relevant factors.
Local and regional governments, as well as economic development agencies, often work to address these challenges and promote economic growth in lower-income areas.
